Data preparation for team category analysis

### 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Removed between day correlations, added supervisor co-location with one team member, whole team co-located, whole team remote, and started rules-based categories

<!-- -   Proportion of working days supervisor is co-located with at least -->
<!--     one team member -->

<!-- -   Proportion of working days entire team is co-located -->

<!-- -   Proportion of working days entire team is remote -->

#### Correlation of work status between days of the week

Three strategies to captured relationships between day are below:

1.  Correlation in telework between days of week

2.  Correlation in status (as an ordered factor) between days of week

3.  Proportion of telework on other days of week, if the employ teleworked on a specific day

##### Correlation in telework between days of week

The script below calculates the correlation in telework between days of the week.

```{r correlation remote only}
prep_day_of_week_cor_telework <- 
  cohort_panel %>% 
  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
  mutate(ind = 1) %>% 
  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
  clean_names() %>% 
  select(person_id,date,date_day_of_week,teleworking) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  mutate(
    date_week_start = floor_date(date,unit = "week")) %>% 
  select(-date) %>% 
  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  clean_names() %>% 
  group_by(person_id) %>%
  # filter(person_id == "10070")
  summarise(
    mon_tue_cor_telework = cor(mon,tue,method = "kendall", use = "complete.obs"),
    mon_wed_cor_telework = cor(mon,wed,method = "kendall", use = "complete.obs"),
    mon_thu_cor_telework = cor(mon,thu,method = "kendall", use = "complete.obs"),
    mon_fri_cor_telework = cor(mon,fri,method = "kendall", use = "complete.obs"),
    tue_wed_cor_telework = cor(tue,wed,method = "kendall", use = "complete.obs"),
    tue_thu_cor_telework = cor(tue,thu,method = "kendall", use = "complete.obs"),
    tue_fri_cor_telework = cor(tue,fri,method = "kendall", use = "complete.obs"),
    wed_thu_cor_telework = cor(wed,thu,method = "kendall", use = "complete.obs"),
    wed_fri_cor_telework = cor(wed,fri,method = "kendall", use = "complete.obs"),
    thu_fri_cor_telework = cor(thu,fri,method = "kendall", use = "complete.obs")
    ) %>% 
  ungroup()
```

Now rename to attach to `prep_building`.

```{r}
prep_xx <- 
  prep_day_of_week_cor_telework
```

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

##### Correlation in status between days of week

The script below calculates the correlation between work status.

```{r correlation ordered status}
prep_day_of_week_cor_status <- 
  cohort_panel %>% 
  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
  mutate(
    daily_status_imputed = fct_lump_prop(daily_status_imputed, prop = .1),
    daily_status_imputed = fct_infreq(daily_status_imputed),
    daily_status_imputed = factor(daily_status_imputed, ordered = TRUE)
  )  %>% 
  mutate(
    date_week_start = floor_date(date,unit = "week")) %>% 
  select(-date) %>% 
  pivot_wider(values_from = daily_status_imputed,names_from = date_day_of_week) %>% 
  mutate(
    across(
      .cols = where(is.factor),
      .fns = ~replace_na(.,"Other")
    )
  ) %>% 
  clean_names() %>% 
  group_by(person_id) %>%
  summarise(
    mon_tue_cor_status = cor(as.numeric(mon),as.numeric(tue),method = "spearman", use = "complete.obs"),
    mon_wed_cor_status = cor(as.numeric(mon),as.numeric(wed),method = "spearman", use = "complete.obs"),
    mon_thu_cor_status = cor(as.numeric(mon),as.numeric(thu),method = "spearman", use = "complete.obs"),
    mon_fri_cor_status = cor(as.numeric(mon),as.numeric(fri),method = "spearman", use = "complete.obs"),
    tue_wed_cor_status = cor(as.numeric(tue),as.numeric(wed),method = "spearman", use = "complete.obs"),
    tue_thu_cor_status = cor(as.numeric(tue),as.numeric(thu),method = "spearman", use = "complete.obs"),
    tue_fri_cor_status = cor(as.numeric(tue),as.numeric(fri),method = "spearman", use = "complete.obs"),
    wed_thu_cor_status = cor(as.numeric(wed),as.numeric(thu),method = "spearman", use = "complete.obs"),
    wed_fri_cor_status = cor(as.numeric(wed),as.numeric(fri),method = "spearman", use = "complete.obs"),
    thu_fri_cor_status = cor(as.numeric(thu),as.numeric(fri),method = "spearman", use = "complete.obs")
    ) %>% 
  ungroup()
```

Now rename to attach to `prep_building`.

```{r}
prep_xx <- 
  prep_day_of_week_cor_status
```

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

##### Proportion of telework week day pairs

First, create a dataframe of telework by days of the week.

```{r proportion remote only prep dataframe}
prep_a <- 
  cohort_panel %>% 
  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
  mutate(ind = 1) %>% 
  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
  clean_names() %>% 
  select(person_id,date,date_day_of_week,teleworking) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  mutate(
    date_week_start = floor_date(date,unit = "week")) %>% 
  select(-date) %>% 
  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  clean_names()
```

Now, a function to calculate the proportion of telework on a different day, if the employee teleworked on a specific day.

```{r}
day_to_day_proportions <- function(in_data,in_var)
{
  var_string <- rlang::as_name(enquo(in_var))

  # print(person_id)

  out <- 
    in_data %>% 
  filter({{in_var}} == 1) %>% 
  group_by(person_id) %>% 
  summarise(
    across(
      .cols = where(is.numeric),
      .fns = ~sum(.,na.rm = TRUE)
  )) %>% 
  mutate(
    across(
      .cols = c(-person_id,-{{in_var}}),
      .fns = ~./{{in_var}},
      .names = "{var_string}_{.col}"
    )
  ) %>% 
  ungroup() %>% 
    select(person_id,starts_with(var_string),-{{in_var}})

Iterated over the days of the week and join results.

```{r}
prep_day_of_week_proportion_pairs <- 
  prep_a %>% 
  select(thu:fri) %>%
  names() %>% 
  map(~day_to_day_proportions(prep_a,!!sym(.))) %>% 
  reduce(full_join, by = "person_id")

Now rename to attach to `prep_building`.

```{r}
prep_xx <- 
  prep_day_of_week_proportion_pairs %>% 
  rename_with(-person_id,
              .fn = ~glue::glue("{.}_prop_pairs")
  )
```

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

#### Modal size of team over observation window

Join to `cohort_panel` only selecting, `person_id`, `date`, and `supervisor_e_mail_address`.

```{r}
prep_b <- 
  cohort_panel %>% 
  select(date,person_id,supervisor_e_mail_address) %>% 
  left_join(prep_a)
```

Calculate the mode team size for each employee.

```{r}
prep_xx <- 
  prep_b %>% 
  group_by(person_id) %>% 
  summarise(team_size_mode = getmode(team_size)) %>% 
  ungroup()
```

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

#### Proportion of working days co-located with at least one other team member

Count dates where co-location occurs by `person_id`.

```{r}
prep_c <- 
  prep_b %>% 
  group_by(person_id) %>% 
  summarise(days_colocated_1 = n_distinct(date)) %>% 
  ungroup()
```

```{r}
prep_xx <- 
  prep_c %>% 
  full_join(prep_building %>% 
              select(person_id,working_days)) %>% 
  mutate(days_colocated_1_working_prop = days_colocated_1/working_days,
         days_colocated_1_observation_prop = days_colocated_1/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days)
```

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

#### Proportion of working days co-located with supervisor

@@

Count dates where co-location with supervisor occurs by `person_id`.

```{r}
prep_c <- 
  prep_b %>% 
  group_by(person_id) %>% 
  summarise(days_colocated_supervisor = n_distinct(date)) %>% 
  ungroup()
```

@@

```{r}
prep_xx <- 
  prep_c %>% 
  full_join(prep_building %>% 
              select(person_id,working_days)) %>% 
  mutate(days_colocated_supervisor_working_prop = days_colocated_supervisor/working_days,
         days_colocated_supervisor_observation_prop = days_colocated_supervisor/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days)
```

@@

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

@@

#### Proportion of working days co-located with entire team

@@

Self left join on `dates`, `location`, and `supervisor_e_mail_address`.

```{r}
prep_b <- 
  prep_a %>% 
  left_join(prep_a,
            by = c("date", "location", "supervisor_e_mail_address"),
            suffix = c("","_joined"))
```

@@

Count number of team members co-located by `person_id` and `date` by counting unique `person_id_joined`.

```{r}
prep_c <- 
  prep_b %>% 
  group_by(person_id,date,supervisor_e_mail_address) %>% 
  summarise(colocated_team_members = n_distinct(person_id_joined)) %>% 
  ungroup()
```

@@

```{r}
prep_d <- 
  cohort_panel %>% 
  group_by(date,supervisor_e_mail_address) %>% 
  summarise(team_size = n_distinct(person_id)) %>% 
  ungroup()
```

@@

```{r}
prep_e <- 
  prep_c %>% 
  left_join(prep_d) %>% 
  filter(colocated_team_members == team_size)
```

@@

Count dates where co-location with whole team occurs by `person_id`.

```{r}
prep_f <- 
  prep_e %>% 
  group_by(person_id) %>% 
  summarise(days_colocated_team = n_distinct(date)) %>% 
  ungroup()
```

Full join `working_days` from `prep_building`, calculate proportion of co-located days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.

```{r}
prep_xx <- 
  prep_f %>% 
  full_join(prep_building %>% 
              select(person_id,working_days)) %>% 
  mutate(days_colocated_team_working_prop = days_colocated_team/working_days,
         days_colocated_team_observation_prop = days_colocated_team/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days)
```

@@

#### Proportion of working days entire team is remote

Identify employees who telework and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.

```{r}
prep_a <-
  cohort_panel %>% 
  filter(daily_status_imputed == "Teleworking") %>%
  select(person_id, date, location, supervisor_e_mail_address) %>%
  distinct()
```

@@

Self left join on `dates`, `location`, and `supervisor_e_mail_address`.

```{r}
prep_b <- 
  prep_a %>% 
  left_join(prep_a,
            by = c("date", "location", "supervisor_e_mail_address"),
            suffix = c("","_joined"))
```

@@

Count number of team members co-located by `person_id` and `date` by counting unique `person_id_joined`.

```{r}
prep_c <- 
  prep_b %>% 
  group_by(person_id,date,supervisor_e_mail_address) %>% 
  summarise(telework_team_members = n_distinct(person_id_joined)) %>% 
  ungroup()
```

@@

```{r}
prep_d <- 
  cohort_panel %>% 
  group_by(date,supervisor_e_mail_address) %>% 
  summarise(team_size = n_distinct(person_id)) %>% 
  ungroup()
```

@@

Left join telework team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when telework team members is the same size as the team

```{r}
prep_e <- 
  prep_c %>% 
  left_join(prep_d) %>% 
  filter(telework_team_members == team_size)
```

@@

Count dates where telework with whole team occurs by `person_id`.

```{r}
prep_f <- 
  prep_e %>% 
  group_by(person_id) %>% 
  summarise(days_telework_team = n_distinct(date)) %>% 
  ungroup()
```

Full join `working_days` from `prep_building`, calculate proportion of telework days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.

```{r}
prep_xx <- 
  prep_f %>% 
  full_join(prep_building %>% 
              select(person_id,working_days)) %>% 
  mutate(days_telework_team_working_prop = days_telework_team/working_days,
         days_telework_team_observation_prop = days_telework_team/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days)
```

@@

The analysis plan defines nine rule-based groups for analysis:

1.  **All remote** - A policy definition for staff that are 100% remote
2.  **Routine teleworker** - Employees with position_category_description's *Onsite Flexible* or *Offsite* that work at least two two days per pay period onsite.
    per pay period onsite.
3.  **Onsite Flexible** - Defined by `position_category_description` in
    the roster data
4.  **Offsite** - Defined by `position_category_description` in the
    roster data
5.  **Onsite Required** - Defined by `position_category_description` in
    the roster data
6.  **Primarily remote** - Employees who work remotely above the 95th
    percentile <!-- could be 75th -->
7.  **Mostly remote** - Employees who work remotely between the median
    and the 95th percentile <!-- could be 75th -->
8.  **Mostly onsite** - Employees who work remotely between 5th
    percentile and the median <!-- could be 25th -->
9.  **Primarily onsite** - Employees who work remotely below the 5th
    percentile <!-- could be 75th -->

@@

```{r}
prep_xx <- 
  prep_building %>% 
  mutate(
    rule_based_all_remote = case_when(
      daily_status_teleworking_working_prop == 1 ~ 1,
                                      TRUE ~ 0)
  ) %>% 
  select(person_id,starts_with("rule_based_"))
```

@@

```{r}
prep_xx <-
  prep_building %>%
  select(
    person_id,
    daily_status_reporting_to_job_site_working_prop,
    daily_status_teleworking_working_prop,
    daily_status_reporting_to_job_site_observation_prop,
    daily_status_teleworking_observation_prop
  ) %>%
  mutate(
    rule_based_primarily_reporting_to_job_site_working =
      case_when(
        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_primarily_teleworking_working =
      case_when(
        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_primarily_reporting_to_job_site_observation =
      case_when(
        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_primarily_teleworking_observation =
      case_when(
        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_reporting_to_job_site_working =
      case_when(
        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_teleworking_working =
      case_when(
        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_reporting_to_job_site_observation =
      case_when(
        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_teleworking_observation =
      case_when(
        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
  ) %>%
  select(person_id, starts_with("rule_based_"))
```

@@

prep_c %>% 
  inner_join(prep_a, by = "person_id") %>% 
  filter(position_category_description.x != position_category_description.y)
```

Identify the `position_category_description` at the beginning of the observation window and convert the categories into indicators.

```{r}
prep_xx <- 
  cohort_first %>% 
  select(person_id,position_category_description) %>% 
  character_to_indicator(in_unique_identifier = "person_id",
                         position_category_description,
                         in_prefix = "rule_based_position_category_")
```

@@

```{r}
prep_xx <- 
  cohort_first %>% 
  select(person_id,position_category_description) %>% 
  left_join(prep_f) %>% 
  mutate(
    rule_based_telework_onsite_minimum = 
      case_when(telework_onsite_minimum == 1 & position_category_description == "Onsite Flexible" ~ 1,
                telework_onsite_minimum == 1 & position_category_description == "Offsite" ~ 1,
                TRUE ~ 0)
  ) %>%
  select(person_id, starts_with("rule_based_"))
```

@@

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

>>>>

### Proportion of working days supervisor is co-located with at least one team member

@@

Count dates where co-location with supervisor occurs by `supervisor_e_mail_address`.

```{r}
prep_c <- 
  prep_b %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(days_colocated_supervisor = n_distinct(date)) %>% 
  ungroup()
```

@@

Full join `working_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days` and `observation_window_days`.

```{r}
prep_xx <- 
  prep_c %>% 
  full_join(prep_building %>% 
              select(supervisor_e_mail_address,working_days,observation_window_days)) %>% 
  mutate(days_colocated_supervisor_working_prop = days_colocated_supervisor/working_days,
         days_colocated_supervisor_observation_prop = days_colocated_supervisor/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days,-observation_window_days)
```

@@

@@

```{r}
prep_building <- 
  prep_building %>% 
  left_join(prep_xx)
```
### Proportion of working days entire team is co-located

@@

Count number of team members co-located by `supervisor_e_mail_address`, `location`, and `date` by counting unique `person_id`.

```{r}
prep_b <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address,location, date) %>% 
  summarise(colocated_team_members = n_distinct(person_id)) %>% 
  ungroup()
```

@@

```{r}
prep_c <- 
  cohort_panel %>% 
  group_by(date,supervisor_e_mail_address) %>% 
  summarise(team_size = n_distinct(person_id)) %>% 
  ungroup()
```

@@

```{r}
prep_d <- 
  prep_b %>% 
  left_join(prep_c) %>% 
  filter(colocated_team_members == team_size)
```

@@

Count dates where co-location with whole team occurs by `supervisor_e_mail_address`.

```{r}
prep_e <- 
  prep_d %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(days_colocated_team = n_distinct(date)) %>% 
  ungroup()
```

@@

Full join `working_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days` and `observation_window_days`.

```{r}
prep_xx <- 
  prep_e %>% 
  full_join(prep_building %>% 
              select(supervisor_e_mail_address,working_days,observation_window_days)) %>% 
  mutate(days_colocated_team_working_prop = days_colocated_team/working_days,
         days_colocated_team_observation_prop = days_colocated_team/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days,-observation_window_days)
```

@@

### Proportion of working days entire team is remote

Identify employees who are teleworking and collect `person_id`, `dates`, and `supervisor_e_mail_address`.

```{r}
prep_a <-
  cohort_panel %>%
  filter(daily_status_imputed == "Teleworking") %>%
  select(person_id, date, supervisor_e_mail_address) %>%
  distinct()
```

@@

Count number of team members co-located by `supervisor_e_mail_address`, and `date` by counting unique `person_id`.

```{r}
prep_b <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address,date) %>% 
  summarise(telework_team_members = n_distinct(person_id)) %>% 
  ungroup()
```

@@

```{r}
prep_c <- 
  cohort_panel %>% 
  group_by(date,supervisor_e_mail_address) %>% 
  summarise(team_size = n_distinct(person_id)) %>% 
  ungroup()
```

@@

Left join teleworking team members and teams size, by `date` and `supervisor_e_mail_address`, then filter to when teleworking team members is the same size as the team.

```{r}
prep_d <- 
  prep_b %>% 
  left_join(prep_c) %>% 
  filter(telework_team_members == team_size)
```

@@

Count dates where co-location with whole team occurs by `supervisor_e_mail_address`.

```{r}
prep_e <- 
  prep_d %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(days_telework_team = n_distinct(date)) %>% 
  ungroup()
```

@@

Full join `team_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with team member by `team_days` and `observation_window_days`, replace nulls with 0, and remove `team_days` and `observation_window_days`.

```{r}
prep_xx <- 
  prep_e %>% 
  full_join(prep_building %>% 
              select(supervisor_e_mail_address,team_days)) %>% 
  mutate(days_telework_team_working_prop =  days_telework_team/team_days,
         days_telework_team_observation_prop = days_telework_team/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-team_days)
```

@@

The analysis plan defines ten rule-based groups for analysis:

1.  **All remote** - All team members are 100% remote
2.  **Routine teleworker** - All team members have
    `position_category_description`'s *Onsite Flexible* or *Offsite* and
    work at least two two days per pay period onsite.
3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
    defined by `position_category_description` in the roster data
4.  **Offsite** - All team members are *Offsite* as defined by team
    members `position_category_description` in the roster data
5.  **Onsite Required** - All team members are *Onsite Required* as
    defined by `position_category_description` in the roster data
6.  **Mixed position categories** - Team members are different position
    categories as as defined by `position_category_description` in the
    roster data
7.  **Primarily remote** - Teams that work remotely above the 95th
    percentile <!-- could be 75th -->
8.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
9.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
10. **Primarily onsite** - Teams that work remotely below the 5th
    percentile <!-- could be 75th -->

@@

```{r}
prep_xx <- 
  prep_building %>% 
  mutate(
    rule_based_all_remote = case_when(
      daily_status_teleworking_working_prop == 1 ~ 1,
                                      TRUE ~ 0)
  ) %>% 
  select(supervisor_e_mail_address,starts_with("rule_based_"))
```

@@

```{r}
prep_xx <-
  prep_building %>%
  select(
    supervisor_e_mail_address,
    daily_status_reporting_to_job_site_working_prop,
    daily_status_teleworking_working_prop,
    daily_status_reporting_to_job_site_observation_prop,
    daily_status_teleworking_observation_prop
  ) %>%
  mutate(
    rule_based_primarily_reporting_to_job_site_working =
      case_when(
        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_primarily_teleworking_working =
      case_when(
        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_primarily_reporting_to_job_site_observation =
      case_when(
        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_primarily_teleworking_observation =
      case_when(
        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_95 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_reporting_to_job_site_working =
      case_when(
        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_teleworking_working =
      case_when(
        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_reporting_to_job_site_observation =
      case_when(
        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
    rule_based_mostly_teleworking_observation =
      case_when(
        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_50 ~ 1,
        TRUE ~ 0
      ),
  ) %>%
  select(supervisor_e_mail_address, starts_with("rule_based_"))
```

@@

prep_c %>% 
  inner_join(prep_b, by = "person_id") %>% 
  filter(position_category_description.x != position_category_description.y)
```

Identify the `position_category_description` at the beginning of the observation window and count number of team members per category by `supervisor_e_mail_address`.

```{r}
prep_a <- 
  cohort_panel %>% 
  group_by(supervisor_e_mail_address,position_category_description) %>% 
  summarise(team_members = n_distinct(person_id)) %>% 
  ungroup() %>% 
  pivot_wider(values_from = team_members, names_from = position_category_description,
              names_prefix = "rule_based_position_category_") %>% 
  clean_names()
```

Inner join with `prep_building` selecting `supervisor_e_mail_address`, and `team_members`.

```{r}
prep_b <- 
  prep_building %>% 
  select(supervisor_e_mail_address,team_members) %>% 
  inner_join(prep_a)
```

Create indicators for when the number of team members equals the number of members in a specific category.

```{r}
prep_c <- 
  prep_b %>% 
  mutate(
    across(
      .cols = starts_with("rule_based_position_category_"),
      .fns = ~case_when(. == team_members ~ 1,
                        TRUE ~ 0)
    )
  )
```

Left join to `prep_building` selecting only `supervisor_e_mail_address` and remove `team_members`.

```{r}
prep_xx <-
  prep_building %>% 
  select(supervisor_e_mail_address) %>% 
  left_join(prep_c) %>% 
  select(-team_members)
```

@@

```{r}
prep_g <- 
  cohort_first %>% 
  select(person_id,position_category_description) %>% 
  left_join(prep_f) %>% 
  mutate(
    rule_based_telework_onsite_minimum = 
      case_when(telework_onsite_minimum == 1 & position_category_description == "Onsite Flexible" ~ 1,
                telework_onsite_minimum == 1 & position_category_description == "Offsite" ~ 1,
                TRUE ~ 0)
  ) %>%
  select(person_id, starts_with("rule_based_"))
```

@@

Left join to `cohort_ids`.

```{r}
prep_h <- 
  cohort_ids %>% 
  left_join(prep_g)
```

```{r}
prep_h %>% 
  skim()
```

```{r}
prep_h %>% 
  filter(rule_based_telework_onsite_minimum == 1) %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id))
```
